The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-11-27 manuscript/manuscript.qmd
Some more rearranging/clarification

- Stats + case study: **Flexibility**
- Stats + case study: **Contentiousness**
- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce)

@@

# Flexibility, contentiousness, and government relationships: The cases of Greenpeace and The Nature Conservancy

Paragraph justifying why the case study is needed

Education, Environment, lower expected operating space (flexibility?)

@@

TODO: Meng - TA vs. RO, exploring main mechanisms of flexibility, contentiousness, and relationships

>>>>

1: issue - stats + case study
2: localness - stats
3: timing - stats

- Stats + case study: **Local**
- Stats + case study: **Contentiousness**
- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce)

@@

# Contentiousness and government relationships: The cases of Greenpeace and The Nature Conservancy

Paragraph justifying why the case study is needed - stats are cool but missing details about contentiousness of issues - also, stats only look at ROs, not TAs or any ONGOs that left the country, so we're missing some dynamics of ONGO-government relations. We can explore our empirical expectations in more depth by looking at a comparative case study of Greenpeace and NC

Education, Environment, lower expected operating space

@@

TODO: Meng - TA vs. RO, exploring main mechanisms of contentiousness, and relationships
